Regular singular Volterra equations on complex domains

### 2023-08-14 reg-sing-volterra.tex
Drop remnants of old layout for results on the prototype solution
Also, revise overview of main result proofs.

Some differential equations pull back to Volterra equations with real-analytic kernels, which extend to holomorphic Volterra equations on complex extensions of the position domain. Solutions that look unrelated in the frequency domain may turn out to be linked by analytic continuation along the complex position domain, as seen in the phenomenon of {\em resurgence} \textcolor{orange}{\cite{EcalleIII}\cite{lectures-marino} \cite[Section 2.4]{sternin1995borel}}.

@@

The prototype solution $\solproto$ is our initial guess. When we apply $\volterra = \hardpart + \softpart$ to it, the singular part $\hardpart$ leaves it unchanged, as we'll show in Section~\ref{sec:construction}. We'll show in Section~\ref{sec:asymptotics} that $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.

@@

When we apply $\volterra$ again, it contracts the perturbation term in $\singexpalg{\tau-1+\epsilon}(\domain)$. More precisely, by making $\Lambda$ large enough, we can ensure that the subspace $\singexp{\tau+1+\epsilon}{\Lambda}(\domain)$ both contains the perturbation term and is contracted by $\volterra$. We'll prove this in Section~\ref{sec:V is a contraction}.

We can now see that at each stage of the Picard iteration process, we have an approximate solution of the form
\[ \solproto + \solptb, \]
with $\solptb \in \singexp{\tau-1+\epsilon}{\Lambda}(\domain)$. Applying $\volterra$ gives us the new approximate solution
\[ \solproto + \softpart \solproto + \volterra \solptb, \]
where the perturbation $\solptb$ has been contracted by $\volterra$ but also augmented with another $\softpart \solproto$. The contraction mapping theorem guarantees that these opposing processes will eventually balance out, bringing us to a unique fixed point where
\[ \solptb = \softpart \solproto + \volterra \solptb. \]
We'll fill out the details of this argument in Section~\ref{sec:existence and uniqueness}.

%%To prove that the Picard iteration process converges, we'll show in Section~\ref{sec:V is a contraction} that $\volterra$ shrinks perturbations

@@

\subsubsection{Construction}\label{sec:construction}
\color{Tomato}
\begin{prop}\label{prop:construction}
    The function 
    \begin{equation}%%\label{eqn:test_solution}
    f_0(a)=\frac{p(b)}{p(a)} \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]
   \end{equation}
is a solution of the Volterra equation $\hardpart f_0=f_0$, for some $b\in\Omega$. We call $f_0$ a prototype solution.  
\end{prop}
\color{black}
\begin{proof}[Proof of Theorem~\ref{thm:basic_volterra}]
    Let $\psi_0(a)= \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]$, then $ d \psi_0 = -\frac{q}{p} \psi_0\;d\zeta $. Hence, for every $a\in\Omega$ 
    \begin{align*}
        \big[\hardpart f_0\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} f_0 d\zeta \\
        &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} \frac{p(b)}{p}\psi_0 d\zeta \\
        &= - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \psi_0 d\zeta\\
        &= \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} d\psi_0  \\
    \end{align*}

@@

\subsubsection{Regularity}\label{sec:asymptotics}

\begin{prop}\label{prop:asymptotic at zero}
    Let $f_0$ be the prototype solution defined in \eqref{eqn:test_solution}, then $|f_0|$ is bounded by a constant multiple of $\zeta^{\tau-1}$ near $\zeta=0$. 
\end{prop}

\begin{proof}
The proof follows the argument we use at the end of the proof of proposition \ref{prop:construction}. In particular, once we choose $\varepsilon>0$ we can choose $\delta>0$ such that for $\zeta(a)<\delta$ and $\zeta(a')<\delta$ the function

@@

The last step uses Condition~\eqref{cond:sing}. 
\end{proof}
\color{Tomato}
\begin{rmk}
   {\em Proposition \ref{prop:construction}} and {\em Proposition \ref{prop:asymptotic at zero}} together prove {\em Theorem \ref{thm:basic_volterra}}. 
\end{rmk}
\color{black}
%In fact, if we assume $q$ to be more regular near $\zeta=0$, we get that $|f_0|/\zeta^{\tau-1}$

\begin{prop}\label{prop:asymptotic at infinity}
    Let $b\in\domain$. Assume $\hardpart$ satisfies {\em Condition} \eqref{cond:slow}. Then the prototype solution $f_0$ constructed in {\em Proposition \ref{prop:construction}} belongs to the function space $\singexp{\tau-1}{\lambda_0}(\domain)$.
\end{prop}
\color{Tomato}
\begin{rmk}
    {\em Proposition \ref{prop:asymptotic at infinity}} is an equivalent formulation of {\em Theorem \ref{thm:proto-growth}}.
\end{rmk}
\color{black}

%%\begin{proof}[Proof of Proposition~\ref{prop:asymptotic at infinity}]
\begin{proof}
We choose $\varepsilon>0$, then by Condition \eqref{cond:sing} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$ (arguing as in the proof of Proposition \ref{prop:asymptotic at zero}) we get a uniform bound

@@

In particular, 
      \begin{align*}
          |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} |f_0|&\leq  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} \left\vert\frac{p(b)}{p(a)}\exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]\right\vert \\
          & \textcolor{magenta}{\lesssim}  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|}  \, e^{\lambda_p|\zeta(a)|}\exp\left[\int_{b}^{a} \Big\vert\frac{q}{p} \Big\vert |d\zeta| \right]\\
          & \textcolor{magenta}{\lesssim}  |\zeta(a)|^{1-\tau} e^{-(\lambda-\lambda_p) |\zeta(a)|} \exp\Big[\lambda_\text{ratio} |\zeta(a)-\zeta(b)| \Big]
      \end{align*}
   which is bounded because $|\zeta(a)|>\delta$.

@@

\begin{prop}\label{prop:get-contraction}
Suppose that $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}. Then, for each $\rho > \tau$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
\end{prop}
\begin{rmk}
For the argument, we'll use, ``big enough'' always requires $\Lambda > \lambda_\Delta$, and may require $\Lambda \gg \lambda_\Delta$.
\end{rmk}
First, pick some $\sigma \in (\tau, \rho)$.\footnote{If you'd like, you can fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By Conditions \eqref{cond:sing} and \eqref{cond:eps-lambda}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
\begin{equation}\label{near-limit}
|k(a, a')| \le \frac{\sigma}{|\zeta(a)|}
\end{equation}
for all $a, a' \in \near$ (see Section~\ref{sec:bounds on k}). By choosing a small enough positive radius $\textcolor{orange}{\delta}$ \textcolor{orange}{[let's choose $R$ or $\delta$ to use both here and in Section~\ref{sec:bounds on k}]}, we can take $\near$ to be the part of $\domain$ where $|\zeta| < \textcolor{orange}{\delta}$. Complementarily, let $\far$ be the part of $\domain$ where $\textcolor{orange}{\delta} \le |\zeta|$.

@@

%The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}=\text{Id}$ for all $\lambda \in (0, \infty)$. This extends the semigroup law:
%\begin{align*}
%\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
%\end{align*}
For all $\nu\in (0,\infty)$, the fractional integral $\fracderiv{-\nu}{\zeta}{\alpha}$ behaves as a Volterra operator $\softpart$ which is singular at $\zeta=\alpha$ but it has a smoothing effect on functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$. In fact, it maps functions $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ to $\fracderiv{-\nu}{\zeta}{\alpha}\varphi\in\singexp{\sigma+\nu}{\Lambda}(\domain_\alpha)$: \textcolor{orange}{[if we want our previous results to apply for a singularity at $\zeta = \alpha$, I think we need to redefine our function spaces for that context]}

\begin{align*}
    \left[\fracderiv{-\nu}{\zeta}{\alpha} \varphi\right](a)&=\frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a (\zeta(a)-\zeta)^{\nu-1} \, \varphi \, d\zeta\\
    &=\frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)- \alpha}\,  \zeta(a)\, \varphi \, d\zeta\\
    &=\frac{\zeta(a)-\alpha}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)- \alpha}\, \varphi \, d\zeta
\end{align*}
Define $\softker(a,a'):=\frac{(\zeta(a)-\zeta(a'))^{\nu-1}}{\zeta(a) - \alpha}$, it is singular at $\zeta(a)=\alpha$ and it satisfies Condition \eqref{cond:eps-lambda} with $\epsilon=\nu-1$ and $\lambda_\Delta=0$, for every $a,a'\in\domain_\alpha$. Hence by Proposition \ref{prop:smoothing}

>>>>

Some differential equations pull back to Volterra equations with real-analytic kernels, which extend to holomorphic Volterra equations on complex extensions of the position domain. Solutions that look unrelated in the frequency domain may turn out to be linked by analytic continuation along the complex position domain, as seen in the phenomenon of {\em resurgence} \cite{EcalleIII}\cite{lectures-marino} \cite[Section 2.4]{sternin1995borel}.

@@

The prototype solution $\solproto$ is our initial guess. When we apply $\volterra = \hardpart + \softpart$ to it, the singular part $\hardpart$ leaves it unchanged, as we'll show in Section~\ref{sec:construction}. In addition, $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$, as shown in Section~\ref{sec:asymptotics}.\textcolor{RoyalBlue}{We'll show in Section~\ref{sec:asymptotics} that $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.}

@@

When we apply $\volterra$ again, it contracts the perturbation term $\solptb$ in $\singexpalg{\tau-1+\epsilon}(\domain)$. More precisely, by making $\Lambda$ large enough, we can ensure that the subspace $\singexp{\tau+1+\epsilon}{\Lambda}(\domain)$ both contains the perturbation term and is contracted by $\volterra$. We'll prove this in Section~\ref{sec:V is a contraction}.

We can now see that at each stage of the Picard iteration process, we start with an approximate solution of the form
\[ \solproto + \solptb, \]
with $\solptb \in \singexp{\tau-1+\epsilon}{\Lambda}(\domain)$. Applying $\volterra$ gives 
\[ \solproto + \softpart \solproto + \volterra \solptb, \]
where the perturbation $\solptb$ has been contracted by $\volterra$, and $\softpart f_0$ has been smoothed and it lies in the same function space as $\solptb$. The contraction mapping theorem guarantees the existence and uniqueness of the fixed point 
\[ \solptb = \softpart \solproto + \volterra \solptb. \]
We'll fill out the details of this argument in Section~\ref{sec:existence and uniqueness}.

\color{RoyalBlue}
We can now see that at each stage of the Picard iteration process, we have an approximate solution of the form
\[ \solproto + \solptb, \]
with $\solptb \in \singexp{\tau-1+\epsilon}{\Lambda}(\domain)$. Applying $\volterra$ gives us the new approximate solution
\[ \solproto + \softpart \solproto + \volterra \solptb, \]
where the perturbation $\solptb$ has been contracted by $\volterra$ but also augmented with another $\softpart \solproto$. The contraction mapping theorem guarantees that these opposing processes will eventually balance out, bringing us to a unique fixed point where
\[ \solptb = \softpart \solproto + \volterra \solptb. \]
We'll fill out the details of this argument in Section~\ref{sec:existence and uniqueness}.
\color{black}
%%To prove that the Picard iteration process converges, we'll show in Section~\ref{sec:V is a contraction} that $\volterra$ shrinks perturbations

@@

\subsubsection{Construction}\label{sec:construction}
\begin{proof}[Proof of Theorem~\ref{thm:basic_volterra}]
    Let $\psi_0(a)= \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]$, then $ d \psi_0 = -\frac{q}{p} \psi_0\;d\zeta $. Hence, for every $a\in\Omega$ 
    \begin{align*}
        \big[\hardpart f_0\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} f_0 d\zeta \\
        &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} \frac{p(b)}{p}\psi_0 d\zeta \\
        &= - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \psi_0 d\zeta\\
        &= \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} d\psi_0  \\
    \end{align*}

@@

\subsubsection{Regularity}\label{sec:asymptotics}
Theorem~\ref{thm:proto-growth} comprises two results with different conditions. We'll prove them separately as Propositions \ref{prop:asymptotic at zero} and \ref{prop:asymptotic at infinity}.
%%\begin{rmk}
%%{\em Propositions \ref{prop:asymptotic at zero}} and \ref{prop:asymptotic at infinity} together prove {\em Theorem \ref{thm:proto-growth}}. 
%%\end{rmk}
\begin{prop}\label{prop:asymptotic at zero}
    Let $f_0$ be the prototype solution defined in \eqref{eqn:test_solution}, then $|f_0|$ is bounded by a constant multiple of $\zeta^{\tau-1}$ near $\zeta=0$. 
\end{prop}

\begin{proof}
The proof follows the argument we use at the end of the proof of Theorem \ref{thm:basic_volterra}. In particular, once we choose $\varepsilon>0$ we can choose $\delta>0$ such that for $\zeta(a)<\delta$ and $\zeta(a')<\delta$ the function

@@

The last step uses Condition~\eqref{cond:sing}. 
\end{proof}
\begin{prop}\label{prop:asymptotic at infinity}
    Let $b\in\domain$. Assume $\hardpart$ satisfies {\em Condition} \eqref{cond:slow}. Then the prototype solution $f_0$ defined in \eqref{eqn:test_solution} belongs to the function space $\singexp{\tau-1}{\lambda_0}(\domain)$.
\end{prop}
\begin{proof}
We choose $\varepsilon>0$, then by Condition \eqref{cond:sing} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$ (arguing as in the proof of Proposition \ref{prop:asymptotic at zero}) we get a uniform bound

@@

In particular, 
      \begin{align*}
          |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} |f_0|&\leq  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} \left\vert\frac{p(b)}{p(a)}\exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]\right\vert \\
          & \lesssim  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|}  \, e^{\lambda_p|\zeta(a)|}\exp\left[\int_{b}^{a} \Big\vert\frac{q}{p} \Big\vert |d\zeta| \right]\\
          & \lesssim  |\zeta(a)|^{1-\tau} e^{-(\lambda-\lambda_p) |\zeta(a)|} \exp\Big[\lambda_\text{ratio} |\zeta(a)-\zeta(b)| \Big]
      \end{align*}
   which is bounded because $|\zeta(a)|>\delta$.

@@

\begin{prop}\label{prop:get-contraction}
Suppose that $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}. Then, for each $\rho > \tau$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
\end{prop}
\begin{rmk}
For the argument, we'll use, ``big enough'' always requires $\Lambda > \lambda_\Delta$, and may require $\Lambda \gg \lambda_\Delta$.
\end{rmk}
First, pick some $\sigma \in (\tau, \rho)$.\footnote{If you'd like, you can fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By Conditions \eqref{cond:sing} and \eqref{cond:eps-lambda}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
\begin{equation}\label{near-limit}
|k(a, a')| \le \frac{\sigma}{|\zeta(a)|}
\end{equation}
for all $a, a' \in \near$ (see Section~\ref{sec:bounds on k}). By choosing a small enough positive radius $\textcolor{orange}{\delta}$, we can take $\near$ to be the part of $\domain$ where $|\zeta| < \textcolor{orange}{\delta}$. Complementarily, let $\far$ be the part of $\domain$ where $\textcolor{orange}{\delta} \le |\zeta|$.

@@

%The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}=\text{Id}$ for all $\lambda \in (0, \infty)$. This extends the semigroup law:
%\begin{align*}
%\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
%\end{align*}
For all $\nu\in (0,\infty)$, the fractional integral $\fracderiv{-\nu}{\zeta}{\alpha}$ behaves as a Volterra operator $\softpart$ which is singular at $\zeta=\alpha$ but it has a smoothing effect on functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$. In fact, it maps functions $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ to $\fracderiv{-\nu}{\zeta}{\alpha}\varphi\in\singexp{\sigma+\nu}{\Lambda}(\domain_\alpha)$: %\textcolor{orange}{[if we want our previous results to apply for a singularity at $\zeta = \alpha$, I think we need to redefine our function spaces for that context]}

\begin{align*}
    \left[\fracderiv{-\nu}{\zeta}{\alpha} \varphi\right](a)&=\frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a (\zeta(a)-\zeta)^{\nu-1} \, \varphi \, d\zeta\\
    &=\frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)- \alpha}\,  \zeta(a)\, \varphi \, d\zeta\\
    &=\frac{\zeta(a)-\alpha}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)- \alpha}\, \varphi \, d\zeta
\end{align*}
Define $\softker(a,a'):=\frac{(\zeta(a)-\zeta(a'))^{\nu-1}}{\zeta(a) - \alpha}$, it is singular at $\zeta(a)=\alpha$ and it satisfies Condition \eqref{cond:eps-lambda} with $\epsilon=\nu-1$ and $\lambda_\Delta=0$, for every $a,a'\in\domain_\alpha$.\footnote{Notice that $\softker$ has a singularity at $\zeta=\alpha$ and not at $\zeta=0$ as in Section \ref{setting:perturbed}. This explains the definition of $\softker(a,a')$ with $\zeta(a)-\alpha$ at the denominator (instead of $\zeta(a)$). More generally, working in the domain $\domain_\alpha$, we'll adapt the conventions used for $\domain$.} Hence by Proposition \ref{prop:smoothing}
